MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-23 ms.tex
Added some compilation images of tp tn bp bn fn fp

%-------------------------------------------------%
\subsection{Failed identifications}\label{sec:failedids}
%-------------------------------------------------%

The best ROC curve, HST:N5ppc32cpb4C100, illustrates that we can lower
the classification threshold and improve the true positive rate by
$\sim10\%$ and sacrifice an increase in false positive rate by
$\lsim5\%$.  In this section, we examine the ``borderline'' images,
which transition from negative classification to positive calculation
in the steepest part of the AUC curve.  Borderline images correspond
to candidates for spectroscopic follow-up.  The model is less
confident about this subset of images, and these would therefore be
good candidates for follow-up human classification and/or
spectroscopic follow-up (CITE HERE???).

\todo{Figure ~\ref{fig:falseids} shows a random sample of 10 borderline
images.  Common features...????}

@@

%

>>>>

%-------------------------------------------------%
\subsection{Image classification performance}\label{sec:performance}
%-------------------------------------------------%

% Defining the 6 paradigms of classification
In this section, we discuss the different image types that our model
is most and least able to successfully classify.  We have six
paradigms of model performance on the mock images, and include a
larger compilation of each of the six image classification paradigms
in the Appendix for the various models we have trained.

% TP and TN
Figure ~\ref{fig:HSTclassificationtile} shows a tile of representative
HST-like images classified with the model, HST:N5ppc32cpb4C100.  The
left column show lensing systems, and right column non-lensing
systems.  From top to bottom, the images are ordered from highest
scoring to lowest scoring with the classification model.  The top left
is what we would call a ``true positive'', a lensing system that will
always classified as positive because of its high score.  Most of the
highest scoring lensing systems exhibit similar extended arcs
\todo{corresponding to a large magnification.}  The bottom right is a
``true negative'', a non-lensing system that will likely be classified
as negative because of its low score.  Many of the lowest scoring
non-lensing systems have \todo{fairly small BCGs, which are non likely
  to lens a background galaxy.}

% FN and FP
The bottom left corresponds to a likely ``false negative,'' or a
lensing system that is likely to be mis-classified as a negative.  The
lowest scoring lensing systems tend to have images with smaller
magnification that are minorly distorted, mimicking the shape of
line-of-sight galaxies that the model has learned to ignore.  The top
right corresponds to a likely ``false positive,'' or a non-lensing
system that is likely to be mis-classified as a positive.  False
positives tend to have ``fuzzy'' along the line of sight galaxies that
mimic lensing arcs.

% BP and BN
The middle row are images whose classification will be most sensitive
to the classification threshold.  We call these borderline images,
with the left corresponding to a ``borderline positive'', and the
right corresponding to a ``borderline negative''.  They sit around the
knee of the ROC curve, the optimal threshold for purity and
completeness.  Note that the ROC curve for HST:N5ppc32cpb4C100
illustrates that we can lower the classification threshold and improve
the true positive rate by $\sim10\%$ and sacrifice an increase in
false positive rate by $\lsim5\%$.  However, small perturbations
around the knee will either include or disinclude the middle row
images.  These are the systems that would make good candidates for
visual and/or spectroscopic follow-up.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering \mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
\caption{HST-like images. The left column corresponds to typical
  lensing systems in our sample from highest scoring (top) to lowest
  scoring, or false negatives (bottom).  The right column corresponds
  to typical non-lensing systems in our sample from highest scoring,
  or false positives (top), to lowest scoring (bottom).  The middle
  row can be considered ``borderline'' classified images, where the
  scores of the lensing and non-lensing system are very close to one
  another.  These are systems that will be most sensitive to the
  classification threshold.}
\label{fig:HSTclassificationtile}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
}

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
}

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
}

\caption{LSST-like images with a BCG. These illustrate the same image
  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
\label{fig:LSSTBCGclassificationtile}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
}

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
}

\mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
        clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
}

\caption{LSST-like images with no BCG. These illustrate the same image
  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
\label{fig:LSSTnoBCGclassificationtile}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Interpreting TP and FP rates
Note that while our training and test set split of $50\%$ lensed and
$50\%$ unlensed images is not realistic, our true positive and false
positive rates in the ROC curves would stay the same for alternative
lensed and unlensed sample splittings.

On the other hand, the ROC curves show a representative rate for lens
and source distributions that are evenly sampled.  The sampling is
{\it not} representative of what we might expect from a an
observational survey.
